%! TeX root = ../analysis-main.tex

\problem{2}{
        Consider the function $f : [0,1] \to \real$ defined by
        \begin{equation*}
                f(x) = \begin{cases}
                        x \log x & x \in (0,1] \\
                        0 & x = 0
                \end{cases}
        \end{equation*}
        \begin{enumerate}[label=(\alph*)]
                \item
                        Is $f$ Lipschitz continuous on $[0,1]$?
                \item
                        Is $f$ uniformly continuous on $[0,1]$?
                \item
                        Suppose $(p_n)$ is a sequence of polynomial functions on $[0,1]$, converging uniformly to $f$.
                        Is the set $A = \{p_n : n \geq 1\} \cup \{f\}$ equicontinuous?
        \end{enumerate}
}

\begin{solution}{Esha Datta, James Hughes, Edgar Jaramillo Rodriguez, Jeonghoon Kim, Van Vinh Nguyen, Qianhui Wan}
        The function is not Lipschitz, to see this note that:
        \[ \lim_{n\to \infty} \frac{f(1/n)-f(0)}{(1/n)-0} = \lim_{n\to\infty} \log(1/n) = -\infty, \]
        so $f$ cannot be Lipschitz.
        However the function is continuous as by L'Hopital's rule:
        \[ \lim_{x\to 0}x\log(x) = \lim_{n\to \infty}\frac{\log(1/n)}{(1/n)} = \lim_{n\to\infty}\frac{1}{n} = 0, \]
        so $f$ is continuous and hence uniformly continuous since we are working over a compact set. 

        For part (c.), fix $\epsilon>0$ and let $N \in \naturals$ be sufficiently large so that $\left\lVert p_n-f \right\rVert < \epsilon/3$.
        Next, since $f$ is uniformly continuous let $\delta>0$ be sufficiently small so that if $|x-y|<\delta$ then $|f(x)-f(y)| < \epsilon/3$.
        Then for all $n>N$, if $|x-y|<\delta$ then:
        \[ |p_n(x)-p_n(y)| \leq |p_n(x)-f(x)|+|f(x)-f(y)|+|f(y)-p_n(y)| \leq 2 \left\lVert p_n-f \right\rVert +|f(x)-f(y)|<\epsilon \]
        Finally, since $p_1,\ldots,p_N$ are each uniformly continuous there exist corresponding $\delta_1,\ldots, \delta_N$ so $\delta_0 = \min\{\delta, \delta_1, \ldots, \delta_N\}$ works for all the $\{p_n\} \cup \{f\}$, hence the set is equicontinuous. 
\end{solution}

\bigskip

\begin{solution}{Kyle Chickering}
	\begin{enumerate}[label=(\alph*)]
    \item
        No. 
        $f'(x)=\log x + 1$ on $(0,1]$, and $\lim_{x\rightarrow 0^+}f'(x) = -\infty$.
        Suppose FSOC that $f$ is Lipschitz with Lipschitz constant $L$, then $|f(x)-f(y)|\leqslant L|x-y|$ for all $x,y\in [0,1]$.
        Choose $x=0$, then we have
        \[ \frac{|f(y)|}{y} \leqslant L \]
        for all $y\in [0,1]$.
        Choose $y=e^{L+1}$, then
        \[ \frac{|e^{L+1}\log e^{L+1}|}{e^{L+1}}= L+1 > L \]
		a contradiction.
        Therefore $f$ is not Lipschitz.

	\item 
        Yes. 
        We will show that $f$ is continuous, and therefore since $f$ is continuous on a compact set $[0,1]$, it is uniformly continuous on $[0,1]$ (Note that this is an explicit example of uniform continuity being weaker than Lipschitz continuity).

		Clearly $x\log x$ is continuous on $(0,1]$ since the product of two continuous functions is continuous.
        By L'Hopital's rule
        \[ \lim_{x\rightarrow 0^+}\frac{\log x}{1/x} = \lim_{x\rightarrow 0^+}x = 0 \]
		so $f$ is continuous on $[0,1]$.

	\item 
        Yes. 
        Let $\epsilon>0$, $x\in [0,1]$ be given and choose $\delta>0$ such that $|f(x)-f(y)| < \epsilon/3 < \epsilon$ whenever $|x-y|<\delta$.
        We will show that $|p_k(x)-p_k(y)|<\epsilon$ whenever $|x-y|<\delta$, for all $k$.
        Choose $N\in \naturals$ such that
        \[ \norm{p_k-f}_{L^\infty}<\frac{\epsilon}{3} \quad \Longrightarrow \quad |p_k(x)-f(x)| < \frac{\epsilon}{3}. \]
        for all $x\in [0,1]$ whenever $k \geqslant N$.
        We set
        \[ A_N:=\{p_k \mid k<N\} \subset A. \]
		It is clear that $A_N$ is equicontinuous since it is a finite collection of uniformly continuous functions (take the infimum of the $\delta$'s).
        Because of this it is clear that if $A\setminus A_N$ is equicontinuous, then so is $A$.
        WLOG we assume $N$ above is 1 and $A_N=\varnothing$.

		We have
		\begin{align*}
			|p_k(x)-p_k(y)| &\leqslant |p_k(x)-f(x)| + |f(x)-f(y)| + |f(y)-p_k(y)| \\
                            &< \frac{\epsilon}{3} + \frac{\epsilon}{3} + \frac{\epsilon}{3} = \epsilon
		\end{align*}
		whenever $|x-y|<\epsilon$ as desired. Therefore $A$ is equicontinuous.
	\end{enumerate}
\end{solution}

